Full title of the paper (Capitalized)

### 2022-03-07 Paper_Draft1/Draft1.Rmd
fixing file paths

```{r table snip, fig.align='center', fig.cap= 'This table is a snippet the data set we will be using.'}
knitr::include_graphics("/Users/elisabethnesmith/womenatthetable/images/table_snippet.png")
```

```{r race plot, fig.align='center', fig.cap= 'This plot shows the distribution of defendant races.'}
knitr::include_graphics("/Users/elisabethnesmith/womenatthetable/images/race_bar_plot.png")
```

```{r age plot, fig.align='center', fig.cap= 'This plot shows the distribution of defendant ages by race.'}
knitr::include_graphics("/Users/elisabethnesmith/womenatthetable/images/race_age_plot.png")
```

```{r recid plot, fig.align='center', fig.cap= 'This plot shows the distribution of two year recidivism outcomes.'}
knitr::include_graphics("/Users/elisabethnesmith/womenatthetable/images/recid_bar_plot.png")
```

```{r recid race plot, fig.align='center', fig.cap= 'This plot shows the distribution of two year recidivism outcomes by race.'}
knitr::include_graphics("/Users/elisabethnesmith/womenatthetable/images/race_recid_plot.png")
```

@@

See Figure \ref{fig:random-plot} below.

```{r random-plot, fig.cap="This is a plot.", fig.align='center'}
plot(rnorm(10), rnorm(10))
```

>>>>

```{r table snip, echo = FALSE, fig.align='center', fig.cap= 'This table is a snippet the data set we will be using.', out.width= "400px", out.height= "200px"}
knitr::include_graphics("../images/table_snippet.png")
```

```{r race plot, echo=FALSE, fig.align='center', fig.cap= 'This plot shows the distribution of defendant races.', out.width= "400px", out.height= "200px"}
knitr::include_graphics("../images/race_bar_plot.png")
```

```{r age plot, echo=FALSE, fig.align='center', fig.cap= 'This plot shows the distribution of defendant ages by race.', out.width= "400px", out.height= "200px"}
knitr::include_graphics("../images/race_age_plot.png")
```

```{r recid plot, echo=FALSE, fig.align='center', fig.cap= 'This plot shows the distribution of two year recidivism outcomes.', out.width= "400px", out.height= "200px"}
knitr::include_graphics("../images/recid_bar_plot.png")
```

```{r recid race plot,echo=FALSE, fig.align='center', fig.cap= 'This plot shows the distribution of two year recidivism outcomes by race.', out.width= "400px", out.height= "200px"}
knitr::include_graphics("../images/race_recid_plot.png")
```

@@

### 2022-03-07 Paper_Draft1/Draft1.tex
fixing file paths

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\OperatorTok{::}\KeywordTok{include_graphics}\NormalTok{(}\StringTok{"/Users/elisabethnesmith/womenatthetable/images/table_snippet.png"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

{\centering \includegraphics[width=27.78in]{/Users/elisabethnesmith/womenatthetable/images/table_snippet}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\OperatorTok{::}\KeywordTok{include_graphics}\NormalTok{(}\StringTok{"/Users/elisabethnesmith/womenatthetable/images/race_bar_plot.png"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

{\centering \includegraphics[width=12.69in]{/Users/elisabethnesmith/womenatthetable/images/race_bar_plot}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\OperatorTok{::}\KeywordTok{include_graphics}\NormalTok{(}\StringTok{"/Users/elisabethnesmith/womenatthetable/images/race_age_plot.png"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

{\centering \includegraphics[width=11.61in]{/Users/elisabethnesmith/womenatthetable/images/race_age_plot}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\OperatorTok{::}\KeywordTok{include_graphics}\NormalTok{(}\StringTok{"/Users/elisabethnesmith/womenatthetable/images/recid_bar_plot.png"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

{\centering \includegraphics[width=11.28in]{/Users/elisabethnesmith/womenatthetable/images/recid_bar_plot}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\OperatorTok{::}\KeywordTok{include_graphics}\NormalTok{(}\StringTok{"/Users/elisabethnesmith/womenatthetable/images/race_recid_plot.png"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

{\centering \includegraphics[width=11.31in]{/Users/elisabethnesmith/womenatthetable/images/race_recid_plot}

@@

See Figure \ref{fig:random-plot} below.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10}\NormalTok{), }\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

{\centering \includegraphics{Draft1_files/figure-latex/random-plot-1}

\caption{This is a plot.}\label{fig:random-plot}
\end{figure}

>>>>

@@

{\centering \includegraphics[width=400px,height=200px]{../images/table_snippet}

@@

@@

{\centering \includegraphics[width=400px,height=200px]{../images/race_bar_plot}

@@

@@

{\centering \includegraphics[width=400px,height=200px]{../images/race_age_plot}

@@

@@

{\centering \includegraphics[width=400px,height=200px]{../images/recid_bar_plot}

@@

@@

{\centering \includegraphics[width=400px,height=200px]{../images/race_recid_plot}

@@
